---
title: "challenge 7 workbook"
author: "Wu Yutong"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,echo=TRUE,eval=TRUE}
library(tidyverse)
library(palmerpenguins)
glimpse(penguins)
```

```{r,echo=TRUE,eval=TRUE}
ggplot(data = penguins, #start with data frame
  mapping = aes(x = bill_depth_mm, #map variables to x and y axis
                y = bill_length_mm,
                colour = species)) + #group by species and represent with colours
  geom_point() + #represent each observation with a point
  labs(title = "Bill depth and length",
      subtitle = "Dimensions for Adelie, Chinstrap, Gentoo",
      x = "Bill depth (mm)", y = "Bill length (mm)",
      colour = "Species",
      caption = "Source: Palmer Station LTER/ palmerpenguins package") + 
  scale_colour_viridis_d() #friendly for colour blindness
```
# manipulate colour 
```{r,echo=TRUE,eval=TRUE}
ggplot(penguins) + aes(x = bill_depth_mm, y = bill_length_mm,
  colour = species) +
    geom_point() + scale_colour_viridis_d()
```

# manipulate shape 
```{r,echo=TRUE,eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species,
        shape = island)) +
  geom_point() + scale_colour_viridis_d()
```

# manipulate size
```{r,echo=TRUE,eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species, shape = species,
      size = body_mass_g)) +
  geom_point() + scale_colour_viridis_d()
```

# manipulate shade
```{r,echo=TRUE,eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species,
        shape = species, size = body_mass_g, alpha = flipper_length_mm)) +
  geom_point() + scale_colour_viridis_d()
```

# mapping vs. setting
mapping is manipulating the geom point for the magnitude of each data point while setting is manipulating for all data points

```{r,echo=TRUE,eval=TRUE}
ggplot(penguins) + 
  aes(x = bill_depth_mm, y = bill_length_mm) + 
  geom_point(size = 2, alpha = 0.5)
```
# faceting
for 2 variables 
```{r,echo=TRUE,eval=TRUE}
ggplot(penguins) + 
  aes(x = bill_depth_mm, y = bill_length_mm) + 
  geom_point() + 
  facet_grid(species ~ island) # (row ~ coloumn)
```

for 1 variable
```{r,echo=TRUE,eval=TRUE}
ggplot(penguins, 
       aes(x = bill_depth_mm, y = bill_length_mm)) + 
  geom_point() + 
  facet_wrap(~ species) # ( ~ coloumn)
```

change how the graph is organised
```{r,echo=TRUE,eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
facet_wrap(~ species, ncol = 2)
```

facet and colour
```{r,echo=TRUE,eval=TRUE}
ggplot(penguins, 
       aes(x = bill_depth_mm, y = bill_length_mm, color = species)) + 
  geom_point() + 
  facet_grid(species ~ sex) + 
  scale_color_viridis_d()
```

remove legend
```{r,echo=TRUE,eval=TRUE}
ggplot(penguins, 
       aes(x = bill_depth_mm, y = bill_length_mm, color = species)) + 
  geom_point() + 
  facet_grid(species ~ sex) + 
  scale_color_viridis_d() +
  guides(color = "none") #remove legend
```

```{r,echo=TRUE,eval=TRUE}
library(openintro)
glimpse(loans_full_schema)
```
selected variables
```{r,echo=TRUE,eval=TRUE}
loans <- loans_full_schema %>%
  select(loan_amount, interest_rate, term, grade, state, annual_income, homeownership, debt_to_income)

glimpse(loans)
```
# histogram
```{r,echo=TRUE,eval=TRUE}
ggplot(loans) + aes(x = loan_amount) +
  geom_histogram()
```
# change binwidth
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = loan_amount)) +
  geom_histogram(binwidth = 1000)
```

# customise histograms
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = loan_amount)) + geom_histogram(binwidth = 5000) +
  labs(x = "Loan amount ($)", y = "Frequency", title = "Amounts of Lending Club loans" )
```

# fill with a categorical value
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
  geom_histogram(binwidth = 5000, alpha = 0.5) +
  labs(x = "Loan amount ($)",y = "Frequency",title = "Amounts of Lending Club loans")
```

# facet with a categorical variable
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) + geom_histogram(binwidth = 5000) +
  labs(x = "Loan amount ($)",y = "Frequency",title = "Amounts of Lending Club loans") +
  facet_wrap(~ homeownership, nrow = 3)
```

# density plot
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = loan_amount)) +
  geom_density()
```

# adjust bandwidth of density plots
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = loan_amount)) +
  geom_density(adjust = 2)
```

# customise density plots
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = loan_amount)) +
  geom_density(adjust = 2) +
  labs( x = "Loan amount ($)", y = "Density", title = "Amounts of Lending Club loans" )
```

# adding a categorical variable 
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
geom_density(adjust = 2, alpha = 0.5) +
labs(x = "Loan amount ($)",y = "Density",title = "Amounts of Lending Club loans", fill = "Homeownership")
```

# boxplot
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = interest_rate)) +
  geom_boxplot()
```

# customizing box plots
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = interest_rate)) +geom_boxplot() +labs(x = "Interest rate (%)",y = NULL,title = "Interest rates of Lending Club loans") +
  theme( axis.ticks.y = element_blank(), axis.text.y = element_blank() )
```

# adding a categoric variable
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = interest_rate,
y = grade)) +
geom_boxplot() +
labs(x = "Interest rate (%)",y = "Grade",title = "Interest rates of Lending Club loans",subtitle = "source")
```

# scatterplot
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
  geom_point()
```

# hex plot
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
  geom_hex()
```

# filter data 
```{r,echo=TRUE,eval=TRUE}
ggplot(loans %>% filter(debt_to_income < 100),
    aes(x = debt_to_income, y = interest_rate)) +
  geom_hex()
```

# bar plot
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = homeownership)) +
  geom_bar()
```

# segmented bar plot
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = homeownership, 
                  fill = grade)) +
geom_bar()
```

# segmented bar plot - by percentage 
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = homeownership, fill = grade)) +
  geom_bar(position = "fill")
```

# customizing bar plots
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(y = homeownership, fill = grade)) + geom_bar(position = "fill") +
labs( x = "Proportion", y = "Homeownership", fill = "Grade", title = "Grades of Lending Club loans")
```

# violin plots
```{r,echo=TRUE,eval=TRUE}
ggplot(loans, aes(x = homeownership, y = loan_amount)) +
  geom_violin()
```

# ridge plots
```{r,echo=TRUE,eval=TRUE}
library(ggridges)

ggplot(loans, aes(x = loan_amount, y = grade, fill = grade, color = grade)) +
  geom_density_ridges(alpha = 0.5)
```
